\documentclass[10pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[top=0.42cm,bottom=0.42cm,left=0.55cm,right=0.55cm]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{mathpazo}
\usepackage{url}

\setlength{\hintscolumnwidth}{0pt}
\setlength{\makecvtitlenamewidth}{8cm}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\renewcommand{\baselinestretch}{0.91}
\renewcommand*{\labelitemi}{\textbullet}

\AtBeginDocument{\recomputelengths}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newlist{resitemize}{itemize}{1}
\setlist[resitemize]{label=\textbullet,leftmargin=*,topsep=0.35mm,itemsep=0.18mm,parsep=0pt,partopsep=0pt}

\newcommand*{\role}[4]{
  \textbf{#1} -- {\itshape #2}\hfill{\small #3 \textbar{} #4}\\[-0.7mm]
}

\newcommand*{\projecttitle}[1]{\vspace{0.8mm}\textbf{#1}\\[-0.9mm]}
\newcommand*{\skillrow}[2]{\textbf{#1} & #2\\[0.35mm]}

\firstname{Kartik}
\familyname{Chauhan}
\address{Bengaluru, India}{}

\begin{document}
\maketitle
\vspace{-12mm}

\begin{center}
\scriptsize
\textbf{Full Stack Engineer \textbar{} AI Engineer \textbar{} Agentic AI Developer}\\[-0.2mm]
\emailsymbol\enspace\emaillink{kartikchauhan336@gmail.com}
\quad \mobilephonesymbol\enspace +91 6396934224
\quad \faHome\enspace\href{https://ranakartikchauhan.in}{ranakartikchauhan.in}\\[-0.3mm]
\faLinkedin\enspace\href{https://linkedin.com/in/ranakartikchauhan}{linkedin.com/in/ranakartikchauhan}
\quad \faGithub\enspace\href{https://github.com/ranakartikchauhan}{github.com/ranakartikchauhan}
\end{center}
\vspace{-4.5mm}

\begin{minipage}[t]{0.66\textwidth}
\footnotesize
\section{Experience}
\role{Associate Delivery Level 3}{SmartData Enterprises Inc.}{Dehradun, Uttarakhand, India}{Jan 2026 -- Present}
\begin{resitemize}
  \item Working on scalable healthcare sector applications with a focus on backend architecture, AI workflows, and enterprise-grade system development.
  \item Developed AI-powered workflows for report generation, audio report processing, automated summarization, and intelligent admin dashboards.
  \item Built scalable backend APIs and optimized data-processing workflows improving system efficiency and reducing manual operations.
  \item Contributed to optimization initiatives that improved API response performance and reduced backend processing overhead by approximately 35\%.
  \item Collaborated with cross-functional teams using Agile methodologies and modern development workflows.
  \item Improved application performance, maintainability, and scalability across multiple production-grade healthcare projects.
\end{resitemize}

\role{Technology Senior Executive}{Pearl Organisation}{Dehradun, Uttarakhand, India}{May 2025 -- Jan 2026}
\begin{resitemize}
  \item Managed and delivered 20+ projects including eCommerce platforms, vehicle booking systems, tour booking applications, and business management solutions.
  \item Handled multiple client projects simultaneously while ensuring timely delivery, production stability, and business-critical workflow support.
  \item Developed scalable web applications and backend services, improving frontend responsiveness through optimized rendering and reusable UI architecture.
  \item Integrated secure payment gateway systems and scalable backend workflows for high-traffic applications while supporting debugging, testing, deployment, and production operations.
\end{resitemize}

\role{Software Developer}{Codementees}{Bengaluru, Karnataka, India}{Sep 2024 -- May 2025}
\begin{resitemize}
  \item Developed a Full-Stack Mentorship Platform using MERN stack, connecting hundreds of mentees with experienced tech mentors.
  \item Built scalable backend APIs supporting authentication, real-time communication, and content management features, including Socket.io messaging that increased engagement by 20\%.
  \item Optimized MongoDB queries, aggregation pipelines, and indexing strategies, improving database performance by 40\% and reducing API response times significantly.
  \item Improved frontend maintainability and performance by building reusable React components, eliminating repetitive code, developing SEO-friendly pages, and applying Next.js server-side rendering best practices.
\end{resitemize}

\role{MERN Stack Developer}{Quitepaper}{Bikaner, Rajasthan, India}{Jul 2023 -- Aug 2024}
\begin{resitemize}
  \item Designed and developed a scalable Library Management System with seat booking and CRM functionality used by multiple organizations.
  \item Engineered backend workflows and optimized query execution to improve booking efficiency and reduce system latency.
  \item Built an automated seat allocation algorithm reducing booking conflicts by 30\% and implemented real-time notifications to improve platform responsiveness.
  \item Integrated secure payment gateway systems capable of handling 1000+ concurrent users using Socket.io, TypeScript, MongoDB, and scalable backend architectures.
\end{resitemize}

\role{Software Engineer Intern}{Canvas Craft Media}{Sahibzada Ajit Singh Nagar, Punjab, India}{Jan 2023 -- May 2023}
\begin{resitemize}
  \item Worked on frontend development using React.js and modern JavaScript frameworks.
  \item Assisted in developing responsive UI components and integrating REST APIs.
  \item Collaborated with senior developers on debugging, testing, feature implementation, full-stack development, and Agile workflows.
\end{resitemize}

\section{Projects}
\projecttitle{AutoNodeAPI -- Open Source NPM Package}
\begin{resitemize}
  \item Developed an open-source Node.js package that automates CRUD API generation for Mongoose models.
  \item Integrated Swagger documentation for automatic API references and improved developer onboarding.
  \item Designed configurable routing and middleware support for scalable backend architecture.
  \item Reduced backend boilerplate code and improved API development speed.
\end{resitemize}

\projecttitle{AI Storytelling \& Agentic Workflow Platform}
\begin{resitemize}
  \item Built AI-powered workflows for automated story generation, image generation, subtitles, and audio creation using LLMs and AI APIs.
  \item Automated multi-step content pipelines reducing manual content generation efforts by approximately 70\%.
  \item Developed agentic AI pipelines using LangChain and LangGraph for multi-step workflow orchestration.
  \item Implemented RAG-based context retrieval systems using vector databases to improve AI response quality.
  \item Integrated OpenAI and Gemini APIs for conversational AI and intelligent automation systems.
\end{resitemize}

\projecttitle{Jobgram}
\begin{resitemize}
  \item Developed a MERN-based job portal platform for recruiters and job seekers.
  \item Implemented advanced filtering, authentication, and recruiter job management workflows.
  \item Built responsive UI components and scalable backend APIs.
  \item \textit{Tech Stack:} React.js, Node.js, Express.js, MongoDB, Vercel.
\end{resitemize}

\end{minipage}
\hfill
\begin{minipage}[t]{0.31\textwidth}
\footnotesize
\section{Professional Summary}
Full-Stack Software Engineer with 3+ years of experience building scalable web applications and AI-powered systems used by thousands of users using the MERN stack and modern AI frameworks. Experienced in high-performance applications, REST APIs, payment systems, real-time architectures, scalable backend architecture, cloud deployment, vector databases, AI automation systems, RAG pipelines, LLM integrations, LangChain, and LangGraph. Improved application performance by up to 40\% through database optimization and scalable frontend engineering, with strong problem-solving skills across production-grade applications and full-stack development.

\section{Skills}
\scriptsize
\begin{tabularx}{\textwidth}{@{}p{16mm}L@{}}
\skillrow{Programming}{JavaScript, TypeScript, Python, C++, SQL, HTML5, CSS3}
\skillrow{Frontend}{React.js, Redux, Tailwind CSS, Bootstrap, Vite}
\skillrow{Backend}{Node.js, Express.js, REST APIs, Socket.io, JWT Authentication}
\skillrow{AI / Agentic AI}{LLMs, LangChain, LangGraph, RAG (Retrieval-Augmented Generation), AI Agents, Prompt Engineering, Vector Databases, AI Workflow Automation, OpenAI APIs, Gemini API, Hugging Face, LangFuse, Multi-Agent Systems, Embeddings, Semantic Search}
\skillrow{Databases}{MongoDB, MySQL, Pinecone, ChromaDB}
\skillrow{Cloud \& DevOps}{AWS, Docker, Kubernetes, Render, GitHub Actions}
\skillrow{Tools}{Git, GitHub, Postman, Swagger, Jira, VS Code}
\end{tabularx}
\footnotesize

\section{Projects Continued}
\projecttitle{TripNest -- Smart Tour \& Vehicle Booking Platform}
\begin{resitemize}
  \item Developed a scalable full-stack travel and booking platform supporting tour booking, vehicle reservations, event booking, and smart travel planning.
  \item Implemented intelligent tour plan suggestions and smart route optimization features to improve user travel experience.
  \item Built a real-time thread and discussion system allowing travelers and organizers to communicate seamlessly.
  \item Integrated secure payment gateway systems capable of handling high concurrent booking traffic.
  \item Developed advanced search filters, booking workflows, admin dashboards, and responsive UI architecture.
  \item Optimized frontend performance using reusable React components and scalable backend APIs.
  \item \textit{Tech Stack:} React.js, Next.js, Node.js, Express.js, MongoDB, Socket.io, Stripe.
\end{resitemize}

\section{Education}
\textbf{Punjab Technical University}\\[-0.3mm]
Bachelor of Technology in Computer Science \& Engineering\\[-0.3mm]
2019 -- 2023

\end{minipage}

\end{document}
